---
title: "Programming Background"
author: "Tommy King"
date: "`r Sys.Date()`"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```
  
```{r Create, echo = TRUE, eval = FALSE}
rmarkdown::render("2022-06-09-Blog-Post-2.Rmd", 
          output_format = "github_document",
          output_dir = "/_posts"
          output_options = list(
            html_preview = FALSE
          )
          )
```

## What R my Thoughts on R?  
  
I would say R is quite unique as far as programming languages go. It feels R's syntax is pretty different from other languages, things like the `<-` operator I think would be considered pretty zany versus other types. I like that it's a scripting language which makes it much easier to play around with as opposed to something you have to run from a file. RStudio also seems like a really easy to use IDE compared to some I've had to use for other languages which is great. You can tell R is open source because there are so many packages out there and some of them feel like almost entirely different languages from each other, but that's also sort of a nice quality because it has a lot of specialized functions and uses. Compared to something like Python I feel like there are slightly fewer examples and help articles out there about R, but that may be something I get better at finding over time.  
  
## R Markdown Output  
  
```{r rmdoutput, eval=TRUE, echo=TRUE }
plot(iris)
```

